RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Efficiency
Inefficiency

\subsection{Proposals that change the hyperparameters and all of the objects}

>>>>

Since this proposal leaves the objects $\{x_i\}$ fixed, it will usually not
affect the value of the likelihood, and therefore the likelihood will not need
to be recomputed.

\subsection{Proposals that change the hyperparameters and all of the objects}
The above proposals allow for changes to $N$, $\alpha$, and $\{x_i\}$,
and are therefore sufficient to allow for ``correct'' exploration of the
prior distribution, and the constrained prior distributions used in DNS.
However, they do not necessarily allow for {\it efficient} exploration, even
of the prior itself. The main reason for this is the inability for large
changes to be made to the hyperparameters $\alpha$.
